\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{titling}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\setlength{\droptitle}{-10em}   % This is your set screw

\title{Experiment Introduction}
\preauthor{}
\postauthor{}
\predate{}
\postdate{}

\date{}
\author{}

\begin{document}
  \maketitle
  \section{Introduction}
  This experiment aims to investigate lie detection inside of virtual environments. You will be placed into a Vive Pro Eye head mounted display. The Vive Pro Eye monitors your eye movement and this experiment will try to use this data to tell if you are lying or not. 
  \section{Procedures}
  You will be provided this document and a small survey. You will then be guided through calibration by a researcher. Then you will run through the experiment. 
  \subsection{Experiment}
  In this experiment you will be placed into a white room. There will be a TV in the room that will both guide you through the experiment and tell prompt you to either lie or tell the truth. You will be allotted a short time period to investigate the room, but after this you will need to focus on the TV as much as possible. You will be asked a question and the TV will tell you to lie or tell the truth. No need to stress about the experiment there will be a short practice session.
  \section{Survey}
  A small survey will be provided for you to fill out. You will answer question about your stances on lying.
  \section{Other Reminders}
  Remember you can stop the experiment at any time without repurcussions. Please keep your own health a priority. 

\end{document}
